Analytics Without Tuning Considered Harmful?

### 2015-08-08 tuningpredictor.tex

\begin{figure}[!t]
\begin{center}
\includegraphics[width=1.5in]{features_precision.eps}\includegraphics[width=1.5in]{features_F.eps}
 \end{center}
\caption{Four representative tuning values in WHERE with  precision and F as tuning goal,respectively. }\label{fig:features}
 \end{figure}

@@

Our exploration of the six research
questions listed in the introduction
show that when learning defect predictors for static code
attributes,   analytics without parameter tuning is considered {\em harmful} and {\em misleading}:
\bi
\item Tuning improves the performance scores of a predictor.
That improvement is usually positive (see \fig{deltas}) and sometimes
it can be quite   dramatic (e.g. precision changing from 2\% to 98\%). \item 
Tuning changes conclusions on what learners are better than others.
Hence, it is time to revisit numerous prior publications of our own~\cite{me07b}
and others~\cite{lessmann2008benchmarking,hall11}.
\item
Also,
tuning changes conclusions on what factors are most important in software development.
Once again, this means that old papers may need to be revised including those
some of our own~\cite{me02k} and others~\cite{bell2013limited,rahman2013how,moser2008comparative,zimmermann2007predicting,herzig2013predicting}. 
\ei
Accordingly, we strongly advise that data miners should not be used ``off-the-shelf'' with their default tunings. 
\wei{remove those two figures here, need to compelete sentence with new ones} show just how much tuning can alter default settings
both for different data sets and for different goals.

>>>>

\begin{figure}[!t]
\begin{center}
\includegraphics[width=1.5in]{features_precision.eps}\includegraphics[width=1.5in]{features_F.eps}
 \end{center}
\caption{Four representative tuning values in WHERE with  precision and F as the tuning goal, respectively. The default values for {\em threshold}, {\em infoPrune}, {\em min\_Size} and {\em wriggle} are $0.5$, $0.33$, $0.5$ and $0.2$.  }\label{fig:features}
 \end{figure}

@@

Our exploration of the six research
questions listed in the introduction
show that when learning defect predictors for static code
attributes,   analytics without parameter tuning is considered {\em harmful} and {\em misleading}:
\bi
\item Tuning improves the performance scores of a predictor.
That improvement is usually positive (see \fig{deltas}) and sometimes
it can be quite   dramatic (e.g. precision changing from 2\% to 98\%). \item 
Tuning changes conclusions on what learners are better than others.
Hence, it is time to revisit numerous prior publications of our own~\cite{me07b}
and others~\cite{lessmann2008benchmarking,hall11}.
\item
Also,
tuning changes conclusions on what factors are most important in software development.
Once again, this means that old papers may need to be revised including those
some of our own~\cite{me02k} and others~\cite{bell2013limited,rahman2013how,moser2008comparative,zimmermann2007predicting,herzig2013predicting}. 
\ei
Accordingly, we strongly advise that data miners should not be used ``off-the-shelf'' with their default tunings. 
\fig{features} shows just how much tuning can alter default settings
both for different data sets and for different goals.
